STR: Seasonal-Trend decomposition using Regression

### 2021-03-31 str_ijds.Rmd
Explanation of some border cases.

Again, by setting the smoothing parameters to zero, some simple special cases are obtained. Setting $\sigma_i$ to zero eliminates the $i$th seasonal component (as it will be equal to zero); setting the variance in the time direction to zero causes the seasonal component to be periodic; setting the variance in the time-season direction to zero causes ????.

>>>>

Again, by setting the smoothing parameters to zero, some simple special cases are obtained.

Setting $\sigma_L$ to zero makes trend linear (as it makes second derivatives equal to zero). On the other hand, setting the variance of the seasonal component in the time-seasonal direction to zero cases the seasonal component to be periodic. By setting both variances to zero we effectively force our model to have a linear trend with seasonal dummies.
Although, setting the variance of the second derivatives of the seasonal component in the time direction to zero alone makes changes in the seasonal component linear over time, but does not preclude the seasonal pattern from changing.
